---
title: "Introduction to chunks"
author: "Antonio Vega"
date: "5/20/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Our own chunk

## Parameters of the chunks

Code |  Meaning                                  
--------------------|--------------------
`echo` | If we match it to `TRUE`, which is the default value, we will be saying that we want the source code of the chunk to be displayed. On the other hand, equal to `FALSE`, it will not be shown
`eval` | If we equate it to `TRUE`, which is the default value, we will be saying that we want the code to be evaluated. On the other hand, equal to `FALSE`, it will not be evaluated
`message` | It allows us to indicate if we want to show the messages that R produces when executing code. Matched to `TRUE` are displayed, matched to` FALSE` no
`warning` | It allows us to indicate if we want to display the warning messages that produce some functions when executed. Matched to `TRUE` are displayed, matched to` FALSE` no

### results parameters

Meaning |  Code  |  Result                                
--------------------|--------------------|--------------------
`results` | `markup` | Default value. It shows us the results in the final document line by line, headed by `##`
`results` | `hide` | The result is not shown in the final document
`results` | `asis` | We return the results line by line literally in the final document and the program with which the final document is opened is interpreted as text and properly formatted
`results` | `hold` | Show all results at the end of the code block

We will calculate $\sqrt{2} - e^{-2}$:

```{R myFirstChunk, echo = TRUE, eval = TRUE}
sqrt(2) - exp(-2)
```

<!-- This will throw a message in this case about the library required -->
<!-- comment=NA will not show the ## -->

```{r magic, message=TRUE, comment=NA}
library(magic)
magic(6)
```

```{r , echo = TRUE, message=TRUE}
library(car)
head(cars,3)
```

When we want to make the square of two:

- In \LaTeX: $\sqrt{2}$
- In `R` doing `r sqrt(2)`
- Combining: $\sqrt{2}=$ `r sqrt(2)`

The number $\pi$ start with `r pi`

## Example using chunk in a paragraph 

To introduce a part of code within a paragraph and to execute it when the document is compiled showing the final result, it must be done using ```r "\u0060r ...\u0060" ```

<div class = "example">
**Example**

The square root of 64 is ```r "\u0060r sqrt(64)\u0060" ``` or, which is the same thing, $\sqrt{64}=$ ```r "\u0060r sqrt(64)\u0060" ```

The fifth root of 32 is `r 32^(1/5)` o, which is the same thing, $\sqrt[5]{64}=$ `r 32^(1/5)`.
</div>

## Another example

```{r check, results="hide", echo=FALSE}
notes = c(3,5,7,7,9,10,4,7,9)
notesMean = mean(notes)
n = length(notes)
desv.tip = sd(notes)
```
This year I have done $n=$ `r n` exams, with an average of $\overline{x}=$ `r round(notesMean,2)` and an standard deviation of $s=$ `r round(desv.tip,2)` 